Supplement

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd

# Supplementary Material {#SupplementaryMaterial}

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}

## Detailed information on psychometric measures {#SupplementQuestionnaires}

*WHO-5.* General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
The german version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].

*Connor-Davidson Resilience Scale.* Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 month[@Sarubin2015].

*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].

*FlexER Scale.* Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
Psychometric properties are currently under investigation.

*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].

*Need for Cognition Scale.* Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994]. Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score. The scale shows comparably high internal consistency (Cronbach's $\alpha>.80$)[@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].

*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used. The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true). It has high internal consistency [Cronbach's $\alpha>.80$; @Schwarzer1999].

*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .

*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].

*Attentional Control Scale.* Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
An internal consistency of Cronbach's $\alpha=.88$ was reported [@Derryberry2002].

## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"

ANOVA:

`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```

## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the arousal rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevView_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrViewPilot)
```

```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevViewPilot)
```

## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"

*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGCorrReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  EMGLevReg_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figures:

```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the corrugator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGCorrRegPilot)
```

```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the levator activity of a single trial. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigEMGLevRegPilot)
```

## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"

ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_pilot_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```

Figure:

```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjEffortPilot)
```

>>>>

```{r child = "Supplement.Rmd"}
```

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGLevView_con[,7], format = "e")`).

To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[2,7])`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared to active viewing.
However, there were no significant differences between strategies (all $p>.05$).
To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing *Corrugator* activity and *Levator* activity of four the strategies.
Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
Post-hoc test revealed reduced *Corrugator* activity during distraction ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[3,7], format = "e")`) compared to active viewing.
There were no significant differences between regulation strategies (all $p>.05$).

>>>>

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator*, and *Levator* activity. 
We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator*, and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see [supplementary material](#SupplementEffectER).

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd

>>>>

## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H")
